%!TEX root = ../thesis.tex
%*******************************************************************************
%*********************************** Research Timelines *****************************
%*******************************************************************************

\chapter{Research Timeline}  %Title of the Research Timeline
The following chapter talks about the research activity timeline conducted for a duration of 2 and half years. 
The plan is subject to change based on any deviation which will be attempted to be covered in the risk analysis 
section. The recent tasks are provided in depth in contrast to later tasks which will be more open ended 
as it reliant to the results from preceding tasks. 

\subsection{Year 2}
This section is split by a month by month planner to help keep tracks of tasks. 

\subsubsection{January 2023}
The high level overview being that most of the setups for the upcoming experiments
are complete. 
\begin{enumerate}
    \item Review of year 1 report submitted 
    \item Setup test cluster for testing popcorn linux 
    \item Setup popcorn linux on the test cluster
    \item Start running existing popcorn linux benchmarks 
    \item Setup RustyHermit and HermitCore independently with test application 
    \item Setup Cheri on a QEMU emulator and run a sample C program 
  \end{enumerate}


  \subsubsection{February 2023}
  \begin{enumerate}
    \item Deep dive understanding to HEXO fork of popcorn linux source code vice.
    \item Setup HEXO offload tasks to a uni-kernel on an external machine using hermit-core 
    and test of 2 more external devices to benchmark the scheduler used by HEXO linux. 
    \item Start working more on porting HermitTux to RustyHermit and look into 
    development of Unikraft for support of Cheri and switch into the Unikraft for further 
    development if there is full support for Cheri. 
    \item Start drafting a conference paper or journal based on improvements to the HEXO papers 
    scheduler and support to either RustyHermit or Unikraft. 
  \end{enumerate}

  \subsubsection{March 2023}
  \begin{enumerate}
    \item Start porting either RustyHermit or Unikraft to support the Cheri Architecture. (The following sub-section is assuming 
          RustyHermit is selected).
          \begin{enumerate}
            \item Making a rust based clone of Hermitux on the rust based rusty-hermit. 
            \item Merging certain C libraries from CheriBSD (or if possible rewriting the C libraries in Rust directly) 
            with the RustyHermit kernel. 
          \end{enumerate}
    \item Investigating having Popcorn modified LLVM C/C++ features with the GHC Haskell compiler. 
  \end{enumerate}

  \subsubsection{April 2023}
  \begin{enumerate}
    \item Continue on making rust based clone of Hermitux on the rust based rusty-hermit and make decision if it's worth going on.
    \item Continue work on the conference paper based on the improvements of the HEXO paper.
    \item Get access to the ARM based Cheri Morello
  \end{enumerate}

  \subsubsection{May 2023}
  \begin{enumerate}
     \item Finalize conference paper/journal paper for improvements based on the HEXO paper.
     \item Start working on merging certain C libraries from CheriBSD (or if possible rewriting the C libraries in Rust directly) 
     with the RustyHermit kernel.
  \end{enumerate}

  \subsubsection{June 2023}
  \begin{enumerate}
     \item Catch up on the pending tasks not completed listed above. 
  \end{enumerate}

  \subsubsection{July 2023}
  \begin{enumerate}
     \item Starting on writing completed research experiments to the thesis. 
  \end{enumerate}

  \subsubsection{August 2023}
  \begin{enumerate}
    \item Summer break 
 \end{enumerate}

 \subsubsection{September 2023}
  \begin{enumerate}
    \item Start modifying Popcorn Linux for building parts of a program to a TAG based architecture.
    \item Start looking into ways to find out which parts of a program should be executed on a TAG based architecture (todo reference
     the paper from popcorn linux on enclaves).
    \item Start drafting proposals that could be used to potentially take the above features of popcorn linux and make a clone of 
    base features which can be used in the GHC Haskell compiler.
 \end{enumerate}

 \subsubsection{October 2023}
  \begin{enumerate}
    \item Continue work on implementing Cheri with popcorn linux using Uni-kernels. 
    \item Start building a test framework to test Cheri with popcorn linux.
 \end{enumerate}

 \subsubsection{November 2023}
  \begin{enumerate}
    \item Reiterate through the literature review and add more background context based on the implementation and experiments 
    completed.
    \item Start working on proposal drafted for adding popcorn linux features to the Haskell GHC compiler.
 \end{enumerate}

 \subsubsection{December 2023}
  \begin{enumerate}
    \item Catch up on pending tasks.
    \item Create benchmark suite for the experiments conducted throughout the year.
    \item Christmas and new year break.
 \end{enumerate}

 \subsubsection{January 2024}
  \begin{enumerate}
    \item Starting writing a conference paper which combines:
    \begin{enumerate}
        \item Multi-kernel approach with a functional language such as Haskell.
        \item With a scheduler such from the HEXO paper with modification to run on TAG based architecture. 
      \end{enumerate}
 \end{enumerate}

 \subsubsection{February 2024}
  \begin{enumerate}
    \item Continue work on the conference paper and complete the draft by the month end.
 \end{enumerate}

 \subsubsection{March 2024}
  \begin{enumerate}
    \item PhD writing period begin.
 \end{enumerate}

 \subsubsection{September 2024}
  \begin{enumerate}
    \item PhD writing period end and Phd thesis draft ready.
 \end{enumerate}




%  \subsubsection{October 2023}
%   \begin{enumerate}
%     \item 
%  \end{enumerate}







